Geometric Information for Image Understanding

### 2018-06-07 chapters/introduction/introduction.tex
add two more references

The topic of understanding images has been around for half a century.
A well known [annodose] in computer vision community is set in the
60s. The MIT professor Dr. Marvin Minsky assigned a couple of
undergrads to spend the summer programming a computer to recognize
objects in the scene~\cite{boden2006mind}. Quite like the attempts of
proving the famous ``Four color theorem'', [[story about a prof claim
he can prove it in a class]]. Fortunate for the mathematicans, the
``Four color theorem'' has been proved by using powerful computational
resources, while the computer scientists are still trapped in Dr.
Marvin Minsky's summer program (not fully solved yet).

The ultimate goal of image understanding is to extract high-level
understanding from digital images or videos. The task seems natural
and easy for an adult human, but it is difficult for machines. 1) Silver
bullet does not exist \todo{cite}, no general algorithm, we do things
in a ad-hoc manner.

The emerge of deep neural network brings light to the dream. The
neural network is a biological design, just like our brains. [history
of neural network]. Data and computational power bring us here.

\brief{Lots algorithm focus on extract high-level info from the images. More
and more deep learning algorithm start identifying lower-level info
from the image like edge extracting and vanishing point detection.
(geometric info). Identifying geometric information is useful for many
applications.}
In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.

Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.

Geometric information can help training neural network to extract
high-level information.

\brief{Specifically, Use of overhead image (or map layout) is useful.
overhead imagery are useful and easy to access, gowing densely
available in space and time.}
The use of overhead imagery has been proved useful for image
understanding.
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

We use geometric information and DL to solve computer vision problems.

>>>>

\brief{
The topic of understanding images has been around for half a century.
A well known [annodose] in computer vision community is set in the
60s. The MIT professor Dr. Marvin Minsky assigned a couple of
undergrads to spend the summer programming a computer to recognize
objects in the scene~\cite{boden2006mind}. Quite like the attempts of
proving the famous ``Four color theorem'', [[story about a prof claim
he can prove it in a class]]. Fortunate for the mathematicans, the
``Four color theorem'' has been proved by using powerful computational
resources, while the computer scientists are still trapped in Dr.
Marvin Minsky's summer program (not fully solved yet).
}

\brief{
The ultimate goal of image understanding is to extract high-level
understanding from digital images or videos. The task seems natural
and easy for an adult human, but it is difficult for machines. 1) Silver
bullet does not exist \todo{cite}, no general algorithm, we do things
in a ad-hoc manner.
}

\brief{
The emerge of deep neural network brings light to the dream. The
neural network is a biological design, just like our brains. [history
of neural network]. Data and computational power bring us here.
}

In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.
%
Lee \etal~\cite{lee2017semantic} propose to detect semantic line
segments, which are able to segment the scene semantically, using
neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
\etal~\cite{yang2016object} explore to detect object contours with
CNNs.
%
Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.

\brief{
Geometric information can help training neural network to extract
high-level information.
}

\todo{re-edit}
The use of overhead imagery has been proved useful for image
understanding.
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

\brief{
We use geometric information and DL to solve computer vision problems.
}
